\cventry{Apr'14 -- Nov'14}
    {Ideabin}
    {}
    {\scriptsize Python (Flask), MySQL (SQLAlchemy), Bootstrap}
    {}
    {
        Developed a website that helps you manage your ideas and share them with people.
        \hfill
        \href{http://github.com/ideabin/ideabin/}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{Sep'13 -- Mar'14}
    {Cryptex}
    {Algorythm'14}
    {\scriptsize PHP, Bootstrap}
    {}
    {
        Created a web based code breaking challenge for our annual fest -- Algorythm.
        \hfill
        \href{http://github.com/jdevlabs/cryptex/}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{}
    {Cheat}
    {}
    {\scriptsize Go}
    {}
    {
        Wrote a tool that allows you to create and view interactive cheatsheets on the command-line. It was designed to help remind *nix system administrators of the commands they use frequently, but keep forgetting.
        \hfill
        \href{http://github.com/dufferzafar/cheat/}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{}
    {Network Usage Monitor}
    {}
    {\scriptsize Python, JavaScript}
    {}
    {
        Created an application to keep track of the amount of network bandwidth being used, and then
        plot the data using d3.js
        \hfill
        \href{https://github.com/dufferzafar/netuse}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{}
    {Fast File Finder}
    {}
    {\scriptsize Python, PyQt}
    {}
    {
        Created a GUI application to find files using the `locate' tool as backend.
        \hfill
        \href{https://github.com/dufferzafar/loki/}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{}
    {Web Based Stuff}
    {}
    {\scriptsize PHP, Angular, Octopress}
    {}
    {
        Have handled a fair share of web based stuff which includes
        blogs (currently based on Octopress),
        an improved interface to search GSoC projects (using Angular.js),
        a PHP based personal website (using metroui.css)
    }
    \vspace*{0.2\baselineskip}

\cventry{}
    {Scripts \& Utilities}
    {}
    {\scriptsize Python, AutoHotkey}
    {}
    {
        Have written numerous little tools that perform tasks like
        sorting downloads,
        uploading screenshots,
        creating automatic music playlists,
        helping me decide what movie to watch,
        tagging my articles-to-read list,
        compressing and backing up data,
        creating a zero-byte disk mirror,
        importing data from iTunes to MusicBrainz, etc.
        \newline
        On Windows, I use an automation language called AutoHotkey, but for the stuff that I need to use on *nix platforms as well, I prefer Python.
        \newline
        \newline
        Most of the above projects, and more, open-sourced at \href{http://github.com/dufferzafar/}{\textcolor{blue}{http://github.com/dufferzafar/}}
    }
    \vspace*{0.2\baselineskip}
