\cventry{Jun'16 -- Sep'16}
    {Software Engineer}
    {Adobe Systems Inc. - Noida}
    {}
    {}
    {
        Worked on automated testing of an Adobe product using Python \& Selenium.
    }
    \vspace*{0.2\baselineskip}

\cventry{Jun'16 -- Aug'16}
    {Student Developer}
    {Google Summer of Code}
    {The Honeynet Project}
    {}
    {
        Ported the codebase of a man-in-the-middle proxy tool called \href{http://github.com/mitmproxy/mitmproxy/}{mitmproxy} from Python 2 to 3. Also improved it's
        code coverage,
        cookie parser,
        export capabilities,
        and terminal UI.
        \hfill
        \href{https://github.com/mitmproxy/mitmproxy/commits?author=dufferzafar}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{Jun'15 -- Aug'15}
    {Student Developer}
    {Google Summer of Code}
    {MetaBrainz Foundation}
    {}
    {
        Improved a Python based music review website called \href{http://critiquebrainz.org/}{CritiqueBrainz}.
        Created an admin interface for it
        and allowed other entities (like musical events) to be reviewed.
        \hfill
        \href{https://github.com/metabrainz/critiquebrainz/commits?author=dufferzafar}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{Dec'14 -- Jan'15}
    {Backend Intern}
    {Cube26 Software Pvt. Ltd}
    {}
    {}
    {
        Worked on prototyping a similarity based image searching algorithm in Python.
    }
    \vspace*{0.2\baselineskip}

\cventry{Jun'14 -- Aug'14}
    {Student Developer}
    {Google Summer of Code}
    {MetaBrainz Foundation}
    {}
    {
        Added features to a music tagging tool and created a website for it.
        \hfill
        \href{https://github.com/metabrainz/picard-website/commits?author=dufferzafar}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}
